The role of aneuploidy in the evolution of cancer drug resistance

### 2023-06-21 EvolutionaryRescue1.tex
started on time section

Even evolutionary rescue occurs, it may take a long time; therefore, it is crucial to estimate the mean waiting time for rescue and the effect aneuploidy may have on it. 
We therefore calculate the mean time for the appearance of the first mutant that rescues the cell population.
This can occur either through the evolutionary trajectory $wildtype \rightarrow mutant$ or through the trajectory $wildtype \rightarrow aneuploid \rightarrow mutant$.
We start with the former.

>>>>

Even if evolutionary rescue occurs, it may take a long time; therefore, it is crucial to estimate the mean waiting time for rescue and the effect aneuploidy may have on it. 
\daniel{I'm not sure about this.}
We therefore calculate the mean time for the appearance of the first mutant that rescues the cell population.
\daniel{Need to be totally clear here that we're conditioning on rescue.}
This can occur either through the evolutionary trajectory $wildtype \rightarrow mutant$ or through the trajectory $wildtype \rightarrow aneuploid \rightarrow mutant$.
We start with the former.
